---
title: "Bryan Acton's CV"
author: Bryan Acton
date: "`r Sys.Date()`"
bibliography: Bryan.bib
csl: apa.csl
nocite: | 
  @acton_putting_2019,
  @acton_built_2020,
  @hansbrough_you_2021,
  @nieberle_leader_2023, 
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(rmarkdown)
require(VennDiagram)
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1FAJbxnIAg5MVLFvW-y54K6KNwBmGsfsJQY5EIrIlUYw",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```

This CV was made by using Nick Strayer's datadrivencv R package, and built in R blogdown

\
```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _bpacton.com/vitae/_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

Main
================================================================================

Bryan Acton {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Publications {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('data_science_writing_aside')
```
:::
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
<div id = "refs"></div>

Working Papers {data-icon=chart-line}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('working_papers')
```


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('research_positions')
```


::: aside
```{r}
CV %<>% print_text_block('industy_experience_aside')
```

:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching_positions')
```


Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('industry_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->
<br>
<br>
<br>

Blogs Written (About)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('blogs')
```


<br>
<br>


Workshops Taught  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('Workshops')
```



Conference Presentations {data-icon=id-badge}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_conferences')
```

::: aside
```{r}
CV %<>% print_text_block('conference_aside')
```
:::

